---
title: "Credit Card Data Analysis"
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
---
###Load library
```{r}
#Factor Analysis
require(psych)
require(GPArotation)
```

###Setting of working Directory and Read Data
```{r}
setwd("C:\\Users\\user\\Desktop\\Credit_card")
cc <- read.csv('CC GENERAL.csv',header = TRUE)
```

###Exploration of Data Tables
```{r}
dim(cc)
str(cc) 
names(cc)
```

###Data Wrangling
```{r}
cc <- cc[-1] #deleting first column
###It is ID which do not carry any information and it bring noise
```

```{r}
cc_func <- function(x){
  nmiss = sum(is.na(x)) #to check total number tof missing values
  a = x[!is.na(x)] #to remove the NA values from dataset
  n = length(a) #length
  m = mean(a) #mean
  min = min(a) #minimum
  max = max(a) #maximum
  s = sd(a) #Standard Deviation
  p1 = quantile(a, 0.95) #Quantile of 95 confidence interval
  p2 = quantile(a, 0.99) #Quantile of 99 confidence interval
  UL = m+3*s #Upper Limit
  LL = m-3*s #Lower Limit
  return(c(n=n, nmiss=nmiss, Mean=m, Min=min, Max=max, StDev=s, P1=p1, P2=p2, 'Upper Limit'=UL, 'Lower Limit'=LL))
}
```


```{r}
vars <- c("BALANCE","BALANCE_FREQUENCY","PURCHASES","ONEOFF_PURCHASES","INSTALLMENTS_PURCHASES",          
          "CASH_ADVANCE","PURCHASES_FREQUENCY","ONEOFF_PURCHASES_FREQUENCY","PURCHASES_INSTALLMENTS_FREQUENCY",
          "CASH_ADVANCE_FREQUENCY","CASH_ADVANCE_TRX","PURCHASES_TRX","CREDIT_LIMIT","PAYMENTS",
          "MINIMUM_PAYMENTS","PRC_FULL_PAYMENT","TENURE") #variable name

```

###Descriptive Statistics
```{r}
describe_stats <- t(data.frame(apply(cc[vars],2,cc_func)))
#Apply Function where {cc[vars]} is variable names,{2} is column to apply, if {1} then apply for row and {cc_func} is function to apply
describe_stats
```


###Data Exploration Plot
```{r}
plotdata<- cc
par(mfrow=c(1,5))
for (i in 1:length(plotdata)) {
        boxplot(plotdata[,i], main=names(plotdata[i]), type="l")

}
```

###outliers treatment
```{r}
cc$BALANCE[cc$BALANCE > 7809.060] <- 7809.060
cc$PURCHASES[cc$PURCHASES > 7413.090] <- 7413.090
cc$ONEOFF_PURCHASES[cc$ONEOFF_PURCHASES > 5572.107] <- 5572.107
cc$INSTALLMENTS_PURCHASES[cc$INSTALLMENTS_PURCHASES > 3124.082] <- 3124.082
cc$CASH_ADVANCE[cc$CASH_ADVANCE > 7270.351] <- 7270.351
cc$CASH_ADVANCE_FREQUENCY[cc$CASH_ADVANCE_FREQUENCY > 0.736] <- 0.736
cc$CASH_ADVANCE_TRX[cc$CASH_ADVANCE_TRX > 23.723] <- 23.723
cc$PURCHASES_TRX[cc$PURCHASES_TRX > 89.283] <- 89.283
cc$CREDIT_LIMIT[cc$CREDIT_LIMIT > 15410.910] <- 15410.910
cc$PAYMENTS[cc$PAYMENTS > 10418.320] <- 10418.320
cc$MINIMUM_PAYMENTS[cc$MINIMUM_PAYMENTS > 7981.557] <- 7981.557
#Eliminating outlier with mean value/median value
```

###Missing value treatment
```{r}
cc$CREDIT_LIMIT[is.na(cc$CREDIT_LIMIT)] <- 4494.4
cc$MINIMUM_PAYMENTS[is.na(cc$MINIMUM_PAYMENTS)] <- 864.20
inputdata <- cc[vars] 
#Omitting missing values with median/mean/mode
```

###correlation of data
```{r}
corr_cc <- cor(inputdata)
corr_cc
```

###Correlation Plot
```{r}
library(corrplot)
corPlot(corr_cc,numbers=TRUE)
```

###Factor Analysis
```{r}
FA <- fa(r = corr_cc, 5, rotate = "varimax", fm = "ml")
FA
```

###Eigen Vectors
```{r}
eigen_value <- eigen(corr_cc)$values
eigen_value
```

###Sorting the factors using factor analysis
```{r}
FA_Sorted <- fa.sort(FA)
ls(FA_Sorted)
loading <- FA_Sorted$loadings
loading
```

###Variable names
```{r}
vars1 <- c("BALANCE","BALANCE_FREQUENCY","PURCHASES","ONEOFF_PURCHASES","PURCHASES_FREQUENCY",
           "PURCHASES_INSTALLMENTS_FREQUENCY","CASH_ADVANCE_TRX","MINIMUM_PAYMENTS")
inputdata1 <- cc[vars1]
head(inputdata1)
```

###Scaling of Data
```{r}
inputdata_final <- scale(inputdata1) #Scaling data ((x-mu)/sd)
head(inputdata_final)
```

###Applying k-means clustering
```{r}
Clus_3 <- kmeans(inputdata_final,3)
Clus_4 <- kmeans(inputdata_final,4)
Clus_5 <- kmeans(inputdata_final,5)
Clus_6 <- kmeans(inputdata_final,6)
```

###Table of clustering
```{r}
table(Clus_3$cluster)
table(Clus_4$cluster)
table(Clus_5$cluster)
table(Clus_6$cluster)
```

###Final Clustering Table of different value of 'k'
```{r}
cc_new <- cbind(cc, Km_Clus_3 = Clus_3$cluster, Km_Clus_4 = Clus_4$cluster, Km_Clus_5 = Clus_5$cluster, Km_Clus_6 = Clus_6$cluster)
cc_new$Km_Clus_3 <- factor(cc_new$Km_Clus_3)
cc_new$Km_Clus_4 <- factor(cc_new$Km_Clus_4)
cc_new$Km_Clus_5 <- factor(cc_new$Km_Clus_5)
cc_new$Km_Clus_6 <- factor(cc_new$Km_Clus_6)

head(cc_new)

```

